---
title: "Importing DBNs to Neo4j"
output: html_notebook
---

I began by creating a folder named DBNdb. By choosing this folder as my database location for Neo4j, it was initialized as a database. I created an import folder within DBNdb and moved desired csv's for importation into the folder. 

Importing GRENITS results into Neo4j:

```{Cypher}

LOAD CSV WITH HEADERS FROM 'file:///prob_above08.csv' AS line
MERGE (a:Gene {name:line.From})
MERGE (b:Gene {name:line.To})
MERGE (a)-[:RELATED_TO {method: "GRENITS", Prob: TOFLOAT( line.Probability), Strength: TOFLOAT(line.Strength)}]->(b);

```

Importing simone results (Network 1) into Neo4j:

```{r}

# Read in relationship csv from simone output. 
defaultNet1 <- read.csv(file.choose(), row.names = 1)

# Read in theta values for relationships from csv from simone output.
defaultNet1Theta <- read.csv(file.choose(), row.names = 1)

# Find indices for 1's in sparse matrix that indicate relationships. 
indexRel <- which(defautlNet1 != 0, arr.ind = T)

# Create data.frame for Genes for importation. 
relGenes <- data.frame(From = rownames(indexRel), 
                       To = colnames(defaultNet1)[indexRel[, 2]])

# Add the R package used to find these relationships as a column. 
relGenes$Method <- rep("simone", dim(relGenes)[1])

# Add theta values to data.frame. 
indexTheta <- which(defaultNet1Theta != 0, arr.ind = T)

# Grab values of theta using the index values. 
Theta <- as.matrix(defaultNet1Theta[indexTheta[, 1], indexTheta[, 2]])

# Append to relGenes data.frame. 
relGenes$Theta <- diag(Theta)

# Write csv to file. 
write.csv(relGenes, file = "simoneDEDBN.csv")

```

Now, I copied the csv into the import file for the database. To import into Neo4j:

```{Cypher}

LOAD CSV WITH HEADERS FROM 'file:///simoneDEDBN.csv' AS line
MERGE (a:Gene {name:line.From})
MERGE (b:Gene {name:line.To})
MERGE (a)-[:RELATED_TO {method: line.Method, Theta: TOFLOAT( line.Theta)}]->(b);

```

Now import simone results (Network 2) by repeatings steps from above.

```{r}

# Read in relationship csv from simone output. 
defaultNet2 <- read.csv(file.choose(), row.names = 1)

# Read in theta values for relationships from csv from simone output.
defaultNet2Theta <- read.csv(file.choose(), row.names = 1)

# Find indices for 1's in sparse matrix that indicate relationships. 
indexRel <- which(defaultNet2 != 0, arr.ind = T)

# Create data.frame for Genes for importation. 
relGenes <- data.frame(From = rownames(indexRel), 
                       To = colnames(defaultNet2)[indexRel[, 2]])

# Add the R package used to find these relationships as a column. 
relGenes$Method <- rep("simone", dim(relGenes)[1])

# Add theta values to data.frame. 
indexTheta <- which(defaultNet2Theta != 0, arr.ind = T)

# Grab values of theta using the index values. 
Theta <- as.matrix(defaultNet2Theta[indexTheta[, 1], indexTheta[, 2]])

# Append to relGenes data.frame. 
relGenes$Theta <- diag(Theta)

# Write csv to file. 
write.csv(relGenes, file = "simoneDEDBN2.csv")

```

Now, I copied the csv into the import file for the database. To import into Neo4j:

```{Cypher}

LOAD CSV WITH HEADERS FROM 'file:///simoneDEDBN2.csv' AS line
MERGE (a:Gene {name:line.From})
MERGE (b:Gene {name:line.To})
MERGE (a)-[:RELATED_TO {method: line.Method, Theta: TOFLOAT( line.Theta)}]->(b);

```

Differences between Network 1 and Network 2 are minimal. Network 2 doesn't need to be included in database. 





